\begin{itemize}
\item \textbf{Senior Data Engineer} \hfill Al-Rajhi Bank \{ARB\}, Riyadh, Saudi Arabia (\textit{January 2025 – Present})
\begin{itemize}
    \item \textbf{Modern Data Stack PoC:} Spearheaded a Proof of Concept to modernize the data architecture using \textbf{Apache Airflow} for orchestration, \textbf{dbt} for transformations, and \textbf{Trino} as the query engine over an \textbf{Apache Iceberg} table format on S3-compatible storage (\textbf{MinIO} and \textbf{OCI Object Storage}).
    \item Developed and optimized ETL mappings and workflows in DEV, SIT, and UAT environments using \textbf{Informatica DEI} and \textbf{Informatica Developer Tool}.
    \item Implemented \textbf{stream-processing pipelines} using \textbf{Kafka/Redpanda}, applying \textbf{distributed systems} principles to ensure scalability, fault tolerance, and high availability.
    \item \textbf{Automation \& Tooling:} Developed Python-based automation suites to:
    \begin{itemize}
        \item Detect and suggest fixes for Informatica DEI issues, reducing troubleshooting time by \textbf{30\%}.
        \item Automate object comparisons between environments, reducing manual validation time by \textbf{40\%}.
        \item Reconcile differences between \textbf{ERwin data models} and physical database schemas (50\% time savings).
    \end{itemize}
    \item Utilized \textbf{PrestoDB/AWS Athena} to execute interactive queries on large-scale datasets in \textbf{AWS S3 data lakes}, supporting critical BI and reporting requirements.
    \item Modeled analytics datasets using \textbf{dimensional modeling} techniques (star and snowflake schemas) and contributed to the design of a centralized \textbf{semantic layer} serving as a single source of truth for \textbf{business metrics} across BI tools.
    \item Collaborated in \textbf{Agile} squads using \textbf{JIRA and Confluence}, ensuring seamless requirement gathering and delivery of cross-functional solutions.
\end{itemize}

\item \textbf{Mid-Levl Data Engineer} \hfill Credit Agricole Egypt, Cairo, Egypt (\textit{December 2023 – December 2024})
\begin{itemize}
    \item  Converted legacy PL/SQL procedures into Informatica PowerCenter mappings and workflows.
    \item  Developed, and tested ETL mappings to consolidate financial data and enhance data accuracy.
    \item  Participated in SIT, UAT, and deployment phases to resolve issues and ensure data integrity across all ETL environments.
    \item  Optimized SQL queries and PL/SQL code to improve performance and reduce execution
\end{itemize}

\item \textbf{Data Engineer} \hfill Banque Misr, Cairo, Egypt ( \textit{June 2022 – March 2023})
\begin{itemize}
    \item Developed and tested OFSAA Funds Transfer Pricing (FTP) methods and cost allocation rules (PFT).
    \item Developed, and tested ETL mappings to consolidate financial data and enhance data accuracy.
    \item Participated in SIT, UAT, and deployment phases to resolve issues and ensure data integrity across all ETL 
    environments.
\end{itemize}

\item \textbf{Junior Data Engineer} \hfill Credit Agricole Egypt, Cairo, Egypt (\textit{August 2021– June 2022})
\begin{itemize}
    \item Developed ETL pipelines using T2T and SCD tools in OFSAA
    \item Built and optimized multiple ETL maps using Informatica PowerCenter to drive OFSAA data warehouse.
    \item Developed, Tested and integrated custom PL/SQL packages, procedures, functions, and triggers to support ETL processes.
    % \item Optimized SQL queries and PL/SQL code to improve performance and reduce execution time.
\end{itemize}

\end{itemize}